The fifteen year struggle of decentralizing privacy-enhancing technology

### 2014-04-03 paper.tex
Whitespace
Added IEEE compsoc header as template
Made table 2 span the whole page otherwise it would not fit
Prevent cutoff in section title on the hyphen in 'privacy-enhancing'
Changed authors and added an extra line in the abstract

% !TeX spellcheck = en_GB
\documentclass{article}
\usepackage{a4wide}

@@

% Title of the paper
\title{The fifteen year struggle of decentralizing privacy-enhancing technology}
% Authors
\author{Rolf Jagerman, Wendo Sab\'ee, Laurens Versluis, Martijn de Vos\\ Supervised by Dr. Ir. Johan Pouwelse}
\date{}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
	Ever since the introduction of the internet, it has been void of any privacy. A number of anonymous communication overlay networks exist whose aim it is to provide privacy to its users. However, due to the nature of the internet, there is major difficulty in getting these networks to become both decentralized and anonymous. We list reasons for having anonymous networks, discern the problems in achieving decentralization and sum up the biggest initiatives in the field and their current status. To do so, we use one exemplary network, the Tor network. We explain how Tor works, what vulnerabilities this network currently has, and possible attacks that could be used to violate privacy and anonymity. The Tor network is used as a key comparison network in the main part of the report: a tabular overview of the major anonymous networking technologies in use today.
\end{abstract}

@@

\section{Decentralized privacy-enhancing systems}
	\label{sec:decentralized}
	Fully decentralized systems with large scale usage are without exception based on the peer-to-peer paradigm. Many such systems have been proposed, yet only some have been implemented and are currently in use and actively maintained \cite{mislove2004ap3, rennhard2002introducing, panchenko2006nisan, rowstron2001pastry, nambiar2006salsa, freedman2002tarzan, ripeanu2001peer, androutsellis2004survey}. Here we focus on fully decentralized networks with the exception of Torsk (which is almost fully decentralized but still requires a neighbourhood authority).

@@

	\begin{table}
		\centering
		\include{tbl-alternativeinternet}
		\caption{The top 10 projects from the Alternative Internet repository by number of commits (as of 2014-03-15).}
		\label{tbl:altinternet}
	\end{table}

>>>>

% !TeX spellcheck = en_GB
\documentclass[12pt,journal,compsoc]{IEEEtran}
%\usepackage{a4wide}

@@

% Title of the paper
\title{The fifteen year struggle of decentralizing privacy-enhancing technology}
% Authors
\author{Rolf Jagerman, Wendo Sab\'ee, Laurens Versluis, Martijn de Vos,\\ Johan Pouwelse (course supervisor)}
\date{}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
	Ever since the introduction of the internet, it has been void of any privacy. The majority of internet traffic currently is and always has been unencrypted. A number of anonymous communication overlay networks exist whose aim it is to provide privacy to its users. However, due to the nature of the internet, there is major difficulty in getting these networks to become both decentralized and anonymous. We list reasons for having anonymous networks, discern the problems in achieving decentralization and sum up the biggest initiatives in the field and their current status. To do so, we use one exemplary network, the Tor network. We explain how Tor works, what vulnerabilities this network currently has, and possible attacks that could be used to violate privacy and anonymity. The Tor network is used as a key comparison network in the main part of the report: a tabular overview of the major anonymous networking technologies in use today.
\end{abstract}

@@

\section{Decentralized privacy-enhancing systems}
	\label{sec:decentralized}

	Fully decentralized systems with large scale usage are without exception based on the peer-to-peer paradigm. Many such systems have been proposed, yet only some have been implemented and are currently in use and actively maintained \cite{mislove2004ap3, rennhard2002introducing, panchenko2006nisan, rowstron2001pastry, nambiar2006salsa, freedman2002tarzan, ripeanu2001peer, androutsellis2004survey}. Here we focus on fully decentralized networks with the exception of Torsk (which is almost fully decentralized but still requires a neighbourhood authority).

@@

	\begin{table*}
		\centering
		\include{tbl-alternativeinternet}
		\caption{The top 10 projects from the Alternative Internet repository by number of commits (as of 2014-03-15).}
		\label{tbl:altinternet}
	\end{table*}
